---
title: "Moonfyre"
author: "Aems_of_Nyx"
date: "2022-09-27"
output: html_document
---


## Purposes

Collect organize some of the R based steps and code utilized in operation moon trees.

```{r}

library("ape")
library("tidytree")
library("tidyverse")
library("ggtree")
library("apTreeshape")

```

### Visualize Tree Recipe and Resources

Theres a python way to do this Dendropy maybe re-evaluate which is the better one at some point.

treedata + ggtrees api see: https://yulab-smu.top/treedata-book/chapter5.html


```{r}

non_herb <- read.tree("simtree.tre")
non_herb2 <- read.tree("gi_best.tre")
non_herb3 <- read.tree("SRR498402_best.tre")

non_herb <- as.treedata(as_tibble(non_herb))
non_herb2 <- as.treedata(as_tibble(non_herb2))

non_herb@phylo$tip.label
non_herb2@phylo$tip.label

ggtree(non_herb)+
  geom_tiplab()+

ggtree(non_herb2)+
  geom_tiplab()

```


### Stats Viz


```{r}

dendOut <- read_delim("dendOut.tsv", delim = "\t")
 
dendOut%>%
  mutate(imbalanceDelt=sackinGen-sackinBase)%>%
  ggplot()+
    geom_density(aes(imbalanceDelt))


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
